Inferring generation-interval distributions from contact tracing data: \\ \emph{in prep, PRSB}

### 2019-03-19 doc/network.tex
meeting

We assume that the disease incidence $i(\tau)$ is the product of the current infectiousness of previously infected individuals and $S(\tau)$, the proportion of the population susceptible.
\jd{Do we need to be clear when we do and don't assume this?}
\begin{equation}
i(\tau) = S(\tau) \int K(s) i(\tau-s) ds = \RR \int g(s) i(\tau-s) ds.
\end{equation}
This model, also referred to as the renewal equation, can represent a wide range of epidemic models \citep{heesterbeek1996concept, diekmann2000mathematical, roberts2004modelling, aldis2005integral, wallinga2007generation, roberts2007model}.
Over a period of time where $S$ remains roughly constant, we would expect approximately exponential growth in $i$; assuming $i(t) = i(0) \exp(r t)$ yields the Euler-Lotka equation \citep{lotka1907relation}, which provides a direct link between speed and strength of an epidemic:
\begin{equation}
\frac{1}{\RR} = \int g(\tau) \exp(-r \tau) d\tau.
\end{equation}

>>>>

\jd{Rewrite these equations a bit more consistently. What are we using for: index infection, current infection? $\tau$ is difference between them. Is it simpler just to use ' for dummies?}
In the homogeneous model, we assume that the disease incidence $i(\tau)$ is the product of the current infectiousness of previously infected individuals and $S(\tau)$, the proportion of the population susceptible.
\begin{equation}
i(\tau) = S(\tau) \int K(s) i(\tau-s) ds = \RR \int g(s) i(\tau-s) ds.
\end{equation}
This model, also referred to as the renewal equation, can represent a wide range of epidemic models \citep{heesterbeek1996concept, diekmann2000mathematical, roberts2004modelling, aldis2005integral, wallinga2007generation, roberts2007model}.
Over a period of time where $S$ remains roughly constant, we would expect approximately exponential growth in $i$; assuming $i(t) = i(0) \exp(r t)$ yields the Euler-Lotka equation \citep{lotka1907relation}, which provides a direct link between speed and strength of an epidemic:
\begin{equation}
\frac{1}{\RR} = \int g(\tau) \exp(-r \tau) d\tau.
\end{equation}
